\documentclass{article}

% Packages required to support encoding
\usepackage{ucs}
\usepackage[utf8x]{inputenc}

% Packages required by code


% Packages always used
\usepackage{hyperref}
\usepackage{xspace}
\usepackage[usenames,dvipsnames]{color}
\hypersetup{colorlinks=true,urlcolor=blue}



\begin{document} 

\vspace{.5em} \hrule \vspace{.5em}
layout: default title: Resume

\hypertarget{group_navigation}{}\subsection*{{group: navigation}}\label{group_navigation}

\hypertarget{dereck_rasmussen}{}\section*{{Dereck Rasmussen}}\label{dereck_rasmussen}

San Francisco, CA - \href{mailto:dereckrx@gmail.com}{email}


\vspace{.5em} \hrule \vspace{.5em}
\hypertarget{software_engineer}{}\subsection*{{Software Engineer}}\label{software_engineer}

Principle Software Engineer with 5+ years of experience working with teams developing product including coding, testing, integration and deployment.


\vspace{.5em} \hrule \vspace{.5em}
\hypertarget{experience}{}\subsection*{{Experience}}\label{experience}

\begin{itemize}%
\item \textbf{\href{http://gainfitness.com}{GAIN Fitness}} (San Francisco, CA)

Co-Founder/Software Engineer, May 2010 - present

\begin{itemize}%
\item Pioneered a concept from spreadsheets and excel models into a functional website and mobile app backend.
\item Worked on all aspects of the project’s development, including front-end design, back-end development, API design, database administration duties, server configuration, and data parsing and processing.

\end{itemize}


\end{itemize}
\begin{itemize}%
\item \textbf{Personal Shopper} (Boise, ID)

Software Engineer, May 2007 - January 2009

\begin{itemize}%
\item Managed all phases of development of internal, web based tools for an e-commerce website.
\item Worked closely with marketing team to define features for managing a large database of products.
\item Added a complex category tree editing feature to a product category management tool, and updated the project to use the Google Web Toolkit.

\end{itemize}


\end{itemize}
\begin{itemize}%
\item \textbf{\href{http://boisestate.edu/}{Boise State University}} (Boise, ID)

\href{http://coen.boisestate.edu/ece/hartman-systems-integration-laboratory/}{Hartman Systems Integration Laboratory}

Research Assistant, January 2006 - December 2006

\begin{itemize}%
\item Programmed Real Time Clock drivers in C using the I2C protocol on small devices.
\item Created a Graphical User Interface to process and display collected sensor data into XML using C# in the .NET environment.

\end{itemize}


\end{itemize}

\vspace{.5em} \hrule \vspace{.5em}
\hypertarget{education}{}\subsection*{{Education}}\label{education}

\begin{itemize}%
\item \textbf{\href{http://boisestate.edu}{Boise State University}} (Boise, ID)

Computer Science, September 2002 - December 2006

\begin{itemize}%
\item Studied algorithms and data structures using Java and object oriented techniques
\item Analysis of object oriented design in C such as modularity, inheritance, encapsulation and object simulation.
\item In depth analysis and comparison of run times for sorting, recursive and iterative algorithms.
\item Programming language analysis involving fundamental differences, along with syntactic and semantic rules.
\item Workflow studies and analysis of the software development lifecycle including development, operation, maintenance and costs.

\end{itemize}


\end{itemize}

\vspace{.5em} \hrule \vspace{.5em}
\hypertarget{skills}{}\subsection*{{Skills}}\label{skills}

\begin{itemize}%
\item Languages

\begin{itemize}%
\item \href{http://www.ruby-lang.org/en/}{Ruby}
\item \href{http://www.java.com/en/}{Java}
\item Javascript
\item HTML5
\item CSS3

\end{itemize}


\end{itemize}
\begin{itemize}%
\item Frameworks/Libraries

\begin{itemize}%
\item \href{http://rubyonrails.org/}{Ruby On Rails}
\item \href{http://jquery.com/}{JQuery}

\end{itemize}


\end{itemize}
\begin{itemize}%
\item Project Technologies

\begin{itemize}%
\item \href{http://www.heroku.com}{Heroku}
\item \href{http://www.postgresql.org/}{Postgresql}
\item \href{http://aws.amazon.com/}{Amazon Web Services} (EC2, S3)
\item \href{http://git-scm.com/}{Git}
\item \href{http://www.google.com/analytics/}{Google Analytics}
\item \href{http://couchdb.apache.org/}{CouchDB}

\end{itemize}


\end{itemize}

\vspace{.5em} \hrule \vspace{.5em}
\hypertarget{interests}{}\subsection*{{Interests}}\label{interests}

\begin{itemize}%
\item Fitness Enthusiast: boxing, circus arts, weightlifting, and biking
\item Discussing and engaging in side projects with friends
\item Body hacking, life hacking and general self-improvement
\item Electronic music, festivals, and Burning Man 2008 & 2009

\end{itemize}

\vspace{.5em} \hrule \vspace{.5em}
\textbf{Download} \href{https://raw.github.com/dereckrx/dereckrx.github.com/master/resume.md}{Plaintext}


\end{document}
